% LaTeX resume using res.cls
\documentclass[margin,10pt]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\setlength{\textwidth}{6in} % set width of text portion
\newcommand{\code}[1]{\texttt{#1}}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames]{color}
%\usepackage[dvipsnames]{xcolor}
\usepackage[bottom]{footmisc}

\definecolor{MidnightBlue}{RGB}{10,82,131} % This replaces the need for xcolor package

\hypersetup{
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=MidnightBlue           % color of external links
}

\usepackage{enumitem}
\setlist[itemize,1]{leftmargin=\dimexpr 26pt-3mm}

\newenvironment{benumerate}[1]{
    \let\oldItem\item
    \def\item{\addtocounter{enumi}{-2}\oldItem}
    \begin{enumerate}
    \setcounter{enumi}{#1}
    \addtocounter{enumi}{1}
}{
    \end{enumerate}
}

% Add fancy footer line with circled page number
\usepackage{fancyhdr}
\usepackage{lipsum}
\usepackage{tikz}
\pagestyle{fancy}
\fancyhf{}
\newcommand*\circled[1]{\tikz[baseline]{\node[shape=circle,draw,inner sep=2pt, line width=1pt] (char) {#1};}}
\fancyfoot[C]{\moveleft\hoffset \hbox{\vbox{\hrule width 0.465\resumewidth height 1pt} \hspace{-2.5mm} \protect\circled{\thepage} \hspace{-2.5mm} \vbox{\hrule width 0.44\resumewidth height 1pt}}}
%\fancyfoot[C]{\moveleft\hoffset \hbox{\vbox{\hrule width 0.465\resumewidth height 0pt} \hspace{-2.5mm} \protect\circled{\thepage} \hspace{-2.5mm} \vbox{\hrule width 0.465\resumewidth height 0pt}}}
\renewcommand{\headrulewidth}{0pt}% Line at the header invisible
\footskip = 5pt

\def\ps@lastpage{%
  \let\@oddhead\@empty\let\@evenhead\@empty%
  \def\@oddfoot{{\slshape\myrev}\hfil\thepage}%
  \def\@evenfoot{{\slshape\myrev}\hfil\thepage}%
  }

\begin{document}

%% Center the name over the entire width of resume:
\moveleft.5\hoffset\centerline{\textsc{\Large Jacob Lustig-Yaeger}}
\moveleft.5\hoffset\centerline{Astronomy \& Astrobiology, PhD}
%
%% Draw a horizontal line the whole width of resume:
\moveleft\hoffset\vbox{\hrule width 0.93\resumewidth height 1pt}
\vspace{-12pt}
\hspace{-1in}
\begin{minipage}[t]{0.93\resumewidth}
Email: \href{mailto:jacob.lustig-yaeger@jhuapl.edu}{jacob.lustig-yaeger@jhuapl.edu} \hfill GitHub: \href{https://github.com/jlustigy}{jlustigy}\\
Web: \url{https://jlustigy.github.io/} \hfill ORCID: \href{https://orcid.org/0000-0002-0746-1980}{0000-0002-0746-1980}
\end{minipage}


%% Select character to use as the bullet marker. 
%% Comment out to get normal dark filled circle bullets
\def\labelitemi{---}	

\begin{resume}

%\section{Current \\Position}
%Exoplanet Post Doctoral Fellow \hfill (2020 -- present)\\
%Johns Hopkins Applied Physics Laboratory \\

\section{Office \\Address}
11100 Johns Hopkins Rd \\
Laurel, MD 20723 \\
United States \\

\section{Education} 
PhD in Astronomy \& Astrobiology (dual-titled PhD) \hfill (2014 -- 2020) \\
MS in Astronomy (2016) \\
University of Washington, Seattle, WA  \\
\textit{Thesis:} \href{https://digital.lib.washington.edu/researchworks/handle/1773/46370}{``The Detection, Characterization, and Retrieval of Terrestrial Exoplanet Atmospheres''} \\
\textit{Advisor:} Professor Victoria Meadows 

BS in Physics (Honors), Minor in Mathematics \hfill (2009 -- 2013) \\
University of California, Santa Cruz, CA \\
\textit{Advisor:} Professor Jonathan Fortney \\

\section{Research \\Interests}
                \begin{itemize}  \itemsep -1pt %reduce space between items
                        \item Characterizing terrestrial exoplanets for habitability and signs of life 
                        \item Retrieving terrestrial planet atmospheres using Bayesian inference 
                        \item Modeling telescope sensitivity to motivate future exoplanet science cases 
                        \item Developing novel methods to detect exoplanet habitability and biosignatures \\
                    \end{itemize}

\section{Research \\Experience} 
                {\sl Post Doctoral Fellow}: The Johns Hopkins Applied Physics Laboratory \hfill (2020 -- present)\\
                Terrestrial exoplanet atmospheres, theory \& observation, mission concepts
                
                {\sl Graduate Research Assistant}: Virtual Planetary Laboratory   \hfill (2014 -- 2020)\\
                Terrestrial exoplanets, their atmospheres, habitability \& biosignatures
                    %\begin{itemize}  \itemsep -1pt %reduce space between items
                    %    \item Developed, tested, and applied a physically rigorous terrestrial exoplanet retrieval model  
                    %    \item Simulated and analyzed radiative transfer, photochemical, climate, telescope, surface mapping, and machine learning models
                    %\end{itemize} 

                {\sl Undergraduate \& Postbaccalaureate Researcher}: University of California, Santa Cruz \hfill          (2012 -- 2014)\\
                Hot Jupiter \& brown dwarf atmospheres, opacity sources, and atmospheric retrieval \\
                    %\begin{itemize}  \itemsep -1pt %reduce space between items
                    %    \item Retrieved exoplanet atmospheric compositions using emission spectra 
                    %    \item Applied Bayesian methods for parameter estimation 
                    %    \item Calculated and published weighted mean opacities for substellar and planetary atmospheres\\
                    %\end{itemize} 
   
\section{Teaching \\Experience} 
                {\sl Research Mentor}: Department of Astronomy, University of Washington \hfill (Sept 2016 -- Present)\\
                Advising undergraduate students in exoplanet astronomy and astrobiology research\\
                \\
                %    \begin{itemize}  \itemsep -1pt %reduce space between items
                %        \item Guadalupe Tovar (UW Undergraduate)
                %    \end{itemize}
                {\sl Teaching Assistant}: Department of Astronomy, University of Washington   \hfill          (Sept 2014 -- June 2015)\\
                Led two biweekly sections for undergraduate students
                    \begin{itemize}  \itemsep -1pt %reduce space between items
                        \item ASTR 101 (Spring 2015; Autumn 2014)
                        \item ASTR 150 (Winter 2015)
                    \end{itemize}  
                
                {\sl Math \& Writing Tutor}: Learning Support Services, UCSC   \hfill          (Sept 2010 -- June 2012)\\
                Instructed students in college level mathematics and writing as a group and drop-in tutor\\
                 
                                  
\section{Honors, Awards, \& Funded Proposals}
                 \begin{itemize}  \itemsep -1pt %reduce space between items
                    %\item Astrobiology Fellow at University of Washington Astrobiology Program (2014)
                    \item \textbf{JWST Cycle 1 Co-PI:} \href{https://www.stsci.edu/jwst/science-execution/program-information?id=1981}{``Tell Me How I’m Supposed To Breathe With No Air: Measuring the Prevalence and Diversity of M-Dwarf Planet Atmospheres''} (2021)
                    \item \textbf{NASA Group Achievement Award:} LUVOIR Mission Concept Study Team (2019)
                    \item Honors undergraduate thesis in physics (2013)
                    \item University Honor, \textit{cum laude} at University of California, Santa Cruz (2013)\\
                 \end{itemize}  
                 
\section{Technical \\Skills} 
                \begin{itemize}  \itemsep -1pt %reduce space between items
                    \item Programming in Python, Julia, IDL, \& Fortran
                    \item Packaging Python code for open-source distribution
                    \item Bayesian parameter inference and model selection 
                    \item Version control and collaboration with git \& GitHub
                    \item Data visualization with Matplotlib, Tableau, \& Bokeh  
                    \item Writing and typesetting with \LaTeX 
                    \item Extensive experience with MS Office Suite \\
                \end{itemize}

\section{Publications} 
                {\sl First Authored}
                \begin{benumerate}{6}
                    \item \textbf{Lustig-Yaeger, J.}, Sotzen, K. S., Stevenson, K. B., Luger, R., May, E. M., Mayorga, L. C., Mandt, K., \& Izenberg, N. R. (2022). \href{https://ui.adsabs.harvard.edu/abs/2022arXiv220200701L/abstract}{``Hierarchical Bayesian Atmospheric Retrieval Modeling for Population Studies of Exoplanet Atmospheres: A Case Study on the Habitable Zone''}. \textit{The Astronomical Journal}.
                    \item \textbf{Lustig-Yaeger, J.}, Stevenson, K. B., Mayorga, L. C., Sotzen, K. S., May, E. M., Izenberg, N. R., \& Mandt, K. (2021). \href{https://doi.org/10.3847/2041-8213/ac2cc2}{``Retrieving Exoplanet Atmospheres using Planetary Infrared Excess: Prospects for the Night side of WASP-43 b and other Hot Jupiters''}. \textit{The Astrophysical Journal Letters}, 921(1), L4.
                    \item \textbf{Lustig-Yaeger, J.}, Meadows, V. S., \& Lincowski, A. P. (2019). \href{https://doi.org/10.3847/2041-8213/ab5965}{``A Mirage of the Cosmic Shoreline: Venus-like Clouds as a Statistical False Positive for Exoplanet Atmospheric Erosion''}. \textit{The Astrophysical Journal Letters}, 887(1), L11. 
                    \item \textbf{Lustig-Yaeger, J.}, Robinson, T. D., \& Arney, G. (2019). \href{https://doi.org/10.21105/joss.01387}{``\texttt{coronagraph}: Telescope Noise Modeling for Exoplanets in Python''}. \textit{Journal of Open Source Software}, 4(40), 1387.
                    \item \textbf{Lustig-Yaeger, J.}, Meadows, V. S., \& Lincowski, A. P. (2019). \href{https://doi.org/10.3847/1538-3881/ab21e0}{``The Detectability and Characterization of the TRAPPIST-1 Exoplanet Atmospheres with JWST''}. \textit{The Astronomical Journal}, 158(1), 27.
                    \item \textbf{Lustig-Yaeger, J.}, Meadows, V. S., Tovar Mendoza, G., Schwieterman, E. W., Fujii, Y., Luger, R., \&  Robinson, T. D. (2018). \href{https://doi.org/10.3847/1538-3881/aaed3a}{``Detecting Ocean Glint on Exoplanets Using Multiphase Mapping''}. \textit{The Astronomical Journal}, 156(6), 301.
                \end{benumerate}
                {\sl Co-Authored}
                \begin{benumerate}{19}
                    \item Komacek, T. D., Kang, W., \textbf{Lustig-Yaeger, J.}, \& Olson, S. L. (2021). \href{https://ui.adsabs.harvard.edu/abs/2021arXiv210808386K/abstract}{``Constraining the Climates of Rocky Exoplanets''}. \textit{Elements}, 17, 4.
                    \item Mayorga, L. C., \textbf{Lustig-Yaeger, J.}, May, E. M., Sotzen, K. S., Gonzalez-Quiles, J., et al. (2021) \href{https://ui.adsabs.harvard.edu/abs/2021PSJ.....2..140M/abstract}{``Transmission Spectroscopy of the Earth-Sun System to Inform the Search for Extrasolar Life''}. \textit{The Planetary Science Journal}, 2(4), 140. 
                    \item Kopparapu, R., Arney, G., Haqq-Misra, \textbf{J., Lustig-Yaeger}, J., \& Villanueva, G. (2021). \href{https://ui.adsabs.harvard.edu/abs/2021ApJ...908..164K/abstract}{``Nitrogen dioxide pollution as a signature of extraterrestrial technology''}. \textit{The Astrophysical Journal}, 908(2), 164.
                    \item $^{\star}$Meadows, V. S., Lincowski, A. P., \& \textbf{Lustig-Yaeger, J.} (2021, $^{\star}$\textit{in prep}). \href{}{``The Feasibility of Detecting Biosignatures in the TRAPPIST-1 Planetary System with JWST''}. % \textit{AAS Journals}.
                    \item Mansfield, M., Schlawin, E., \textbf{Lustig-Yaeger, J.}, et al. (2020). \href{https://ui.adsabs.harvard.edu/abs/2020MNRAS.499.5151M/abstract}{``Eigenspectra: A Framework for Identifying Spectra from 3D Eclipse Mapping''}. \textit{Monthly Notices of the Royal Astronomical Society}.
                    \item Leung, M., Meadows, V. S., \& \textbf{Lustig-Yaeger, J.} (2020). \href{https://ui.adsabs.harvard.edu/abs/2020arXiv200413731L/abstract}{``High-Resolution Spectral Discriminants of Ocean Loss for M Dwarf Terrestrial Exoplanets''}. \textit{The Astronomical Journal}, 160(1), 11. 
                    \item Chouqar, J., Zouhair, B., Jabiri, A., \textbf{Lustig-Yaeger, J.}, Soubkiou, A., \& Szentgyorgyi, A. (2020). \href{https://ui.adsabs.harvard.edu/abs/2020MNRAS.495..962C/abstract}{``Properties of Sub-Neptune Atmospheres: TOI-270 System''}. \textit{Monthly Notices of the Royal Astronomical Society}, 495(1), 962-970.
                    \item Guzewich, S. D., \textbf{Lustig-Yaeger, J.}, Davis, C. E., Kopparapu, R. K., Way, M. J., \& Meadows, V. S.  (2020). \href{https://ui.adsabs.harvard.edu/abs/2020arXiv200202549G/abstract}{``The Impact of Planetary Rotation Rate on the Reflectance and Thermal Emission Spectrum of Terrestrial Exoplanets Around Sun-like Stars''}. \textit{The Astrophysical Journal}, 893, 140. 
                    \item Lincowski, A. P., \textbf{Lustig-Yaeger, J.}, \& Meadows, V. S.  (2019). \href{https://doi.org/10.3847/1538-3881/ab2385}{``Observing Isotopologue Bands in Terrestrial Exoplanet Atmospheres with the James Webb Space Telescope---Implications for Identifying Past Atmospheric and Ocean Loss''}. \textit{The Astronomical Journal}, 158(1), 26.
                    \item Luger, R., Agol, E., Foreman-Mackey, D., Fleming, D. P., \textbf{Lustig-Yaeger, J.}, \& Deitrick, R. (2019).  \href{http://adsabs.harvard.edu/cgi-bin/bib_query?arXiv:1810.06559}{``STARRY: Analytic Occultation Light Curves''}. \textit{The Astronomical Journal}, 157(2), 64.
                    \item Lincowski, A. P., Meadows, V. S., Crisp, D., Robinson, T. D., Luger, R., \textbf{Lustig-Yaeger, J.}, \& Arney, G.N. (2018). \href{http://adsabs.harvard.edu/cgi-bin/bib_query?arXiv:1809.07498}{``Evolved Climates and Observational Discriminants for the TRAPPIST-1 Planetary System''}. \textit{The Astrophysical Journal}, 867(1), 76.
                    \item Meadows, V. S.,  Reinhard, C. T., Arney, G. N., Parenteau, M. N., Schwieterman, E. W., Domagal-Goldman, S. D., Lincowski, A. P., Stapelfeldt, K. R., Rauer, H., DasSarma, S., Hegde, S., Narita, N., Deitrick, R., \textbf{Lustig-Yaeger, J.}, Lyons, T. W., \& Siegler, N. (2018).  \href{http://adsabs.harvard.edu/abs/2018AsBio..18..630M}{``Exoplanet Biosignatures:  Understanding Oxygen as a Biosignature in the Context of Its Environment''}. \textit{Astrobiology}, 18, 630-662.
                    \item Meadows, V. S., Arney, G. N., Schwieterman, E. W., \textbf{Lustig-Yaeger, J.}, Lincowski, A. P., Robinson, T.,  Domagal-Goldman, S. D., Barnes, R. K., Fleming, D. P., Deitrick, R., Luger, R., Driscoll, P. E., Quinn, T. R., Crisp, D. (2018). \href{http://adsabs.harvard.edu/abs/2018AsBio..18..133M}{``The Habitability of Proxima Centauri b: Environmental States and Observational Discriminants''}. \textit{Astrobiology}, 18, 133-189.
                    \item Luger, R., \textbf{Lustig-Yaeger, J.}, \& Agol, E. (2017).  \href{http://adsabs.harvard.edu/abs/2017ApJ...851...94L}{``Planet-Planet Occultations in TRAPPIST-1 and Other Exoplanet Systems''}. \textit{The Astrophysical Journal}, 851(2), 94.
                    \item Fujii, Y., \textbf{Lustig-Yaeger, J.}, \& Cowan, N. B. (2017). \href{http://adsabs.harvard.edu/abs/2017arXiv170804886F}{``Rotational Spectral Unmixing of Exoplanets: Degeneracies between Surface Colors and Geography''}. \textit{The Astronomical Journal}, 154(5), 189.
                    \item Luger, R., \textbf{Lustig-Yaeger, J.}, Fleming, D. P., Tilley, M. A., Agol, E, Meadows, V. S., Deitrick, R., \& Barnes, R. (2017). \href{http://adsabs.harvard.edu/abs/2017ApJ...837...63L}{``The Pale Green Dot: A Method to Characterize Proxima Centauri b using Exo-Aurorae''}. \textit{The Astrophysical Journal}, 837, 63.
                    \item Barnes, R., Deitrick, R., Luger, R., Driscoll, P. E., Quinn, T. R., Fleming, D. P., Arney, G., Crisp, D., Domagal-Goldman, S. D., Lincowski, A. P., \textbf{Lustig-Yaeger, J.}, \& Schwieterman, E. (2017). \href{http://adsabs.harvard.edu/cgi-bin/bib_query?arXiv:1608.06919}{``The Habitability of Proxima Centauri b I: Evolutionary Scenarios''}. \textit{arXiv preprint arXiv:1608.06919.}
                    \item Greene, T. P., Line, M. R., Montero, C., Fortney, J. J., \textbf{Lustig-Yaeger, J.}, \& Luther, K. (2016). \href{http://adsabs.harvard.edu/abs/2016ApJ...817...17G}{``Characterizing transiting exoplanet atmospheres with JWST''}. \textit{The Astrophysical Journal}, 817(1), 17.
                    \item Freedman, R. S., \textbf{Lustig-Yaeger, J.}, Fortney, J. J., Lupu, R. E., Marley, M. S., \& Lodders, K. (2014). \href{http://adsabs.harvard.edu/abs/2014ApJS..214...25F}{``Gaseous Mean Opacities for Giant Planet and Ultracool Dwarf Atmospheres over a Range of Metallicities and Temperatures''}. \textit{The Astrophysical Journal Supplement Series}, 214(2), 25.\\
                \end{benumerate}
                %{\sl Non-Peer Reviewed}
                %\begin{benumerate}{1}
                %    \item Barnes, R., Deitrick, R., Luger, R., Driscoll, P. E., Quinn, T. R., Fleming, D. P., Arney, G., Crisp, D., Domagal-Goldman, S. D., Lincowski, A. P., \textbf{Lustig-Yaeger, J.}, \& Schwieterman, E. (2017). \href{http://adsabs.harvard.edu/cgi-bin/bib_query?arXiv:1608.06919}{``The Habitability of Proxima Centauri b I: Evolutionary Scenarios''}. \textit{arXiv preprint arXiv:1608.06919.}\\
                %\end{benumerate}
                 
                 
\section{Conference \\Presentations} 
                {\sl Invited Talks}
                \begin{benumerate}{4}
                    \item \textbf{Lustig-Yaeger, J.} \& Meadows, V. S.\ (2019). 
                    \href{https://agu.confex.com/agu/fm19/meetingapp.cgi/Paper/639372}{``The Era of Terrestrial Exoplanet Characterization''}. AGU, Joint AGU-AAS Session on Frontiers in Exoplanets, San Francisco, CA, 10 Dec. \href{https://www.youtube.com/watch?v=DDPguEQPPos}{\textit{Watch it on YouTube!}}
                    \item \textbf{Lustig-Yaeger, J.}, Meadows, V. S., \& Lincowski, A. P.\ (2019). \href{https://seec.gsfc.nasa.gov/Symposium.html}{``Prospects for Biosignatures for Rocky Planets in the Era of JWST''}. SEEC Symposium 2019, ``Rocky Exoplanets in the Era of JWST: Theory and Observation'', NASA Goddard, Greenbelt, MD, 5 Nov. 
                    \item \textbf{Lustig-Yaeger, J.}, Meadows, V. S., \& Lincowski, A. P.\ (2019). \href{https://exoplanets.nasa.gov/exep/events/270/exopag-20/}{``The Detectability and Characterization of the TRAPPIST-1 Exoplanet Atmospheres with JWST''}. ExoPAG 20, Bellevue, WA, 23 Jun.
                    \item \textbf{Lustig-Yaeger, J.}, Meadows, V., Tovar, G., Schwieterman, E., \& Fujii, Y.\ ``Prospects for Mapping Terrestrial Exoplanets with LUVOIR''. Goddard Space Flight Center, October 25, 2017
                \end{benumerate}
                {\sl Contributed Talks}
                \begin{benumerate}{7}
                    \item \textbf{Lustig-Yaeger, J.}, Meadows, V. S., \& Lincowski, A. P.\ (2019). \href{https://docs.google.com/viewer?url=https://agu.confex.com/agu/abscicon19/mediafile/ExtendedAbstract/Paper481632/JLY_AbSciCon2019_Abstract3.pdf}{``TRAPPIST-1 and Beyond: Strategies for Characterizing Terrestrial Exoplanets and their Habitability''}. Abstract [202-7] presented at 2019 Astrobiology Science Conference, Bellevue, WA, 24-28 June. 
                    \item \textbf{Lustig-Yaeger, J.}, Meadows, V. S., \& Lincowski, A. P.\ (2019). ``Detecting and Characterizing Terrestrial Atmospheres in the TRAPPIST-1 System with JWST''. TRAPPIST-1 Conference, Li\`ege, Belgium, 11-14 Jun. 
                    \item \textbf{Lustig-Yaeger, J.}, Meadows, V. S., \& Lincowski, A. P.\ (2019). \href{http://adsabs.harvard.edu/abs/2019AAS...23310303L}{``Simulating the Detectability and Characterization of the TRAPPIST-1 Exoplanet Atmospheres with JWST''}. American Astronomical Society Meeting Abstracts, 233, \#103.03
                    \item \textbf{Lustig-Yaeger, J.}, Meadows, V. S., Tovar, G., Schwieterman, E., W., Fujii, Y., Luger, R., \& Robinson, T. D.\ (2018). \href{https://agu.confex.com/agu/fm18/prelim.cgi/Paper/384157}{``Detecting Oceans on Exoplanets with Next-Generation Telescopes''}. 2018 AGU Fall Meeting, Washington, D.C., 10-14 Dec. P51B-09
                    \item \textbf{Lustig-Yaeger, J.}, Luger, R., \& Agol, E. (2017). \href{https://www.hou.usra.edu/meetings/habitableworlds2017/pdf/4100.pdf}{``Probing the Orbital Dynamics and Atmospheric Properties of the TRAPPIST-1 Planets with JWST''}. Habitable Worlds 2017, \#4100
                    \item \textbf{Lustig-Yaeger, J.}, Tovar, G., Fujii, Y., Schwieterman, E., \& Meadows, V.\ (2017). \href{http://www.lpi.usra.edu/meetings/abscicon2017/pdf/3558.pdf}{``Mapping Surfaces and Clouds on Terrestrial Exoplanets Observed with Next-Generation Coronagraph-Equipped Telescopes''}. Astrobiology Science Conference, \#3558
                    \item \textbf{Lustig-Yaeger, J.}, Line, M.~R., \& Fortney, J.~J.\ (2015). \href{http://adsabs.harvard.edu/abs/2015AAS...22512403L}{``On the Confidence of Molecular Detections in the Atmospheres of Exoplanets from Secondary Eclipse Spectra''}. American Astronomical Society Meeting Abstracts, 225, \#124.03\\ 
                \end{benumerate}
                
                {\sl Posters}
                \begin{benumerate}{8}  
                    \item \textbf{Lustig-Yaeger, J.}, Lincowski, A. P., \& Meadows, V. S. (2017). \href{https://www.hou.usra.edu/meetings/habitableworlds2017/pdf/4098.pdf}{``Extending Atmospheric Characterization to Earth-Sized Exoplanets with JWST: Transits, Eclipses, and the TRAPPIST-1 System''}. Habitable Worlds 2017, Laramie, WY \#4098
                    \item \textbf{Lustig-Yaeger, J.}, Tovar, G., Schwieterman, E. W., Fujii, Y., \& Meadows, V. S. (2017). \href{https://www.hou.usra.edu/meetings/habitableworlds2017/pdf/4110.pdf}{``Detecting Oceans on Exoplanets Using Phase-Dependent Mapping with Next-Generation Coronagraph-Equipped Telescopes''}. Habitable Worlds 2017, Laramie, WY \#4110
                    \item \textbf{Lustig-Yaeger, J.}, Schwieterman, E., Meadows, V., \& Fujii, Y. (2016). \href{http://adsabs.harvard.edu/abs/2016DPS....4812234L}{``Modeling Earth's Disk-Integrated, Time-Dependent Spectrum: Applications to Directly Imaged Habitable Planets''}. AAS/Division for Planetary Sciences Meeting Abstracts, 48, \#122.34
                    \item \textbf{Lustig-Yaeger, J.}, Meadows, V., Schwieterman, E. W., \& Robinson, T. (2016). \href{http://www.exoplanetscience.org/speakers}{``Modeling Earth’s Disk-Integrated Spectrum through a Lunar Month: 
                    Applications to Directly Imaged Habitable Exoplanets''}. Exoplanets I
                    \item \textbf{Lustig-Yaeger, J.}, Meadows, V., Line, M., \& Crisp, D.\ (2015). \href{http://adsabs.harvard.edu/abs/2015DPS....4741610L}{``A Novel Approach to Atmospheric Retrieval for Small Exoplanets''}. AAS/Division for Planetary Sciences Meeting Abstracts, 47, \#416.10
                    \item \textbf{Lustig-Yaeger, J.}, Line, M., Fortney, J.~J., \& Meadows, V.\ (2015). \href{http://www.hou.usra.edu/meetings/abscicon2015/pdf/7558.pdf}{``Detecting Molecules in Exoplanet Atmospheres: Lessons Learned from Hot Jupiters''}. Astrobiology Science Conference, \#7558
                    \item \textbf{Lustig-Yaeger, J.},  Line, M.~R., \& Fortney, J.~J.\ (2014). \href{http://www2.lowell.edu/workshops/coolstars18/abstracts-posters/poster-abstract-267.html}{``On the Detection Significance of Molecules in Exoplanets from Secondary Eclipse Observations''}. Cool Stars, 18, \#267
                    \item \textbf{Lustig-Yaeger, J.}, Fortney, J.~J., Freedman, R., Marley, M.~S., \& Lupu, R.~E.\ (2014). \href{http://adsabs.harvard.edu/abs/2014AAS...22334704L}{``Gaseous Mean Opacities for Giant Planet and Brown Dwarf Atmospheres''}. American Astronomical Society Meeting Abstracts \#223, \#347.04\\
                 \end{benumerate}
                 
 \section{Public Talks}
                \begin{itemize}  
                    \item ``Proxima Centauri b: A World of Possibilities'' and panel discussion with Guillem Anglada-Escude, Rory Barnes, \& Olivier Guyon, UW Astrobiology \& the NASA Astrobiology Institute Lecture Series, Seattle, WA. May 3, 2017.
                    \item ``BREAKING: Terrestrial Exoplanet Discovered in the Habitable Zone of Proxima Centauri'' Astronomy on Tap, Peddler Brewing Company, Seattle, WA. August 24, 2016.\\
                 \end{itemize}
                 
\section{Press}
                \begin{itemize}  
                    \item University of Washington, Seattle. (2019, August 13). \href{https://www.washington.edu/news/2019/08/13/james-webb-space-telescope-could-begin-learning-about-trappist-1-atmospheres-in-a-single-year-study-indicates/}{``James Webb Space Telescope could begin learning about TRAPPIST-1 atmospheres in a single year, study indicates''} [Press release]. 
                 \end{itemize}

%\AtEndDocument{\vfill%
\hfill \textit{Last updated on \today}
%}

\end{resume}
\end{document}
