% LaTeX resume using res.cls
\documentclass[margin,10pt]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\setlength{\textwidth}{6in} % set width of text portion
\newcommand{\code}[1]{\texttt{#1}}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames]{color}
%\usepackage[dvipsnames]{xcolor}

\definecolor{MidnightBlue}{RGB}{10,82,131} % This replaces the need for xcolor package

\hypersetup{
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=MidnightBlue           % color of external links
}

\usepackage{enumitem}
\setlist[itemize,1]{leftmargin=\dimexpr 26pt-3mm}

\newenvironment{benumerate}[1]{
    \let\oldItem\item
    \def\item{\addtocounter{enumi}{-2}\oldItem}
    \begin{enumerate}
    \setcounter{enumi}{#1}
    \addtocounter{enumi}{1}
}{
    \end{enumerate}
}

\begin{document}

%% Center the name over the entire width of resume:
\moveleft.5\hoffset\centerline{\textsc{\Large Jacob Lustig-Yaeger}}
\moveleft.5\hoffset\centerline{Curriculum Vitae}
%
%% Draw a horizontal line the whole width of resume:
\moveleft\hoffset\vbox{\hrule width 0.93\resumewidth height 1pt}
\vspace{-12pt}
\hspace{-1in}
\begin{minipage}[t]{0.93\resumewidth}
Email: \href{mailto:jlustigy@uw.edu}{jlustigy@uw.edu} \hfill GitHub: \href{https://github.com/jlustigy}{jlustigy}\\
Web: \url{http://staff.washington.edu/jlustigy/}
\end{minipage}


%% Select character to use as the bullet marker. 
%% Comment out to get normal dark filled circle bullets
\def\labelitemi{---}	

\begin{resume}

\section{Office \\Address}
Department of Astronomy, University of Washington \\
Physics-Astronomy Bldg, B319 \\
Box 351580 \\
Seattle, WA 98195-1580 \\

\section{Education} 
University of Washington, Seattle, WA \hfill 2014 --\\
Graduate student in Astronomy and Astrobiology (dual-title PhD program)  

University of Washington, Seattle, WA \hfill 2014 -- 2016\\
M. Sci. in Astronomy

University of California, Santa Cruz, CA  \hfill 2009 -- 2013\\
B.S.\ with Honors in Physics \\
Minor in Mathematics\\

\section{Research \\Experience} 
                {\sl Graduate Research Assistant}: Virtual Planetary Laboratory   \hfill          Sept 2014 --\\
                Extrasolar planets, their atmospheres, \& habitability with Dr. Victoria Meadows
                    \begin{itemize}  \itemsep -1pt %reduce space between items
                        \item Lead developer of a retrieval model for the analysis of terrestrial exoplanet spectra 
                        \item Experience simulating and analyzing radiative transfer, photochemical, climate, telescope noise, and exoplanet mapping models
                        \item Programming in Python, Julia, IDL, \& Fortran
                    \end{itemize}  

                {\sl Junior Specialist}: University of California, Santa Cruz \hfill          Dec 2013 -- Aug 2014\\
                Hot Jupiter atmospheres with Dr. Jonathan Fortney and Dr. Michael Line
                    \begin{itemize}  \itemsep -1pt %reduce space between items
                        \item Wrote Python code to analyze the emission spectra of exoplanets observed during secondary eclipse
                        \item Gained experience using Bayesian methods of parameter estimation
                    \end{itemize}  
                    
\section{Honors \\ \& Awards}
                 \begin{itemize}  \itemsep -1pt %reduce space between items
                    %\item Astrobiology Fellow at University of Washington Astrobiology Program (2014)
                    \item Honors undergraduate thesis in physics (2013)
                    \item University Honor, \textit{cum laude} at University of California, Santa Cruz (2013)\\
                 \end{itemize}  

\section{Selected \\ Publications} 
                \begin{benumerate}{5}
                    %\item Meadows, V. S.,  Reinhard, C. T., Arney, G. N., Parenteau, M. N., Schwieterman, E. W., Domagal-Goldman, S. D., Lincowski, A. P., Stapelfeldt, K. R., Rauer, H., DasSarma, S., Hegde, S., Narita, N., Deitrick, R., \textbf{Lustig-Yaeger, J.}, Lyons, T. W., \& Siegler, N. (2018).  \href{http://adsabs.harvard.edu/abs/2018AsBio..18..630M}{``Exoplanet Biosignatures:  Understanding Oxygen as a Biosignature in the Context of Its Environment''}. \textit{Astrobiology}, 18, 630-662.
                    \item Meadows, V. S., Arney, G. N., Schwieterman, E. W., \textbf{Lustig-Yaeger, J.}, Lincowski, A. P., Robinson, T.,  Domagal-Goldman, S. D., Barnes, R. K., Fleming, D. P., Deitrick, R., Luger, R., Driscoll, P. E., Quinn, T. R., Crisp, D. (2018). \href{http://adsabs.harvard.edu/abs/2018AsBio..18..133M}{``The Habitability of Proxima Centauri b: Environmental States and Observational Discriminants''}. \textit{Astrobiology}, 18, 133-189.
                    \item Luger, R., \textbf{Lustig-Yaeger, J.}, \& Agol, E. (2017).  \href{http://adsabs.harvard.edu/abs/2017ApJ...851...94L}{``Planet-Planet Occultations in TRAPPIST-1 and Other Exoplanet Systems''}. \textit{The Astrophysical Journal}, 851(2), 94.
                    \item Fujii, Y., \textbf{Lustig-Yaeger, J.}, \& Cowan, N. B. (2017). \href{http://adsabs.harvard.edu/abs/2017arXiv170804886F}{``Rotational Spectral Unmixing of Exoplanets: Degeneracies between Surface Colors and Geography''}. \textit{The Astronomical Journal}, 154(5), 189.
                    \item Luger, R., \textbf{Lustig-Yaeger, J.}, Fleming, D. P., Tilley, M. A., Agol, E, Meadows, V. S., Deitrick, R., \& Barnes, R. (2017). \href{http://adsabs.harvard.edu/abs/2017ApJ...837...63L}{``The Pale Green Dot: A Method to Characterize Proxima Centauri b using Exo-Aurorae''}. \textit{The Astrophysical Journal}, 837, 63.
                    %\item Barnes, R., Deitrick, R., Luger, R., Driscoll, P. E., Quinn, T. R., Fleming, D. P., Arney, G., Crisp, D., Domagal-Goldman, S. D., Lincowski, A. P., \textbf{Lustig-Yaeger, J.}, \& Schwieterman, E. (2017). \href{http://adsabs.harvard.edu/cgi-bin/bib_query?arXiv:1608.06919}{``The Habitability of Proxima Centauri b I: Evolutionary Scenarios''}. \textit{arXiv preprint arXiv:1608.06919.}
                    \item Greene, T. P., Line, M. R., Montero, C., Fortney, J. J., \textbf{Lustig-Yaeger, J.}, \& Luther, K. (2016). \href{http://adsabs.harvard.edu/abs/2016ApJ...817...17G}{``Characterizing transiting exoplanet atmospheres with JWST''}. \textit{The Astrophysical Journal}, 817(1), 17.
                    %\item Freedman, R. S., \textbf{Lustig-Yaeger, J.}, Fortney, J. J., Lupu, R. E., Marley, M. S., \& Lodders, K. (2014). \href{http://adsabs.harvard.edu/abs/2014ApJS..214...25F}{``Gaseous Mean Opacities for Giant Planet and Ultracool Dwarf Atmospheres over a Range of Metallicities and Temperatures''}. \textit{The Astrophysical Journal Supplement Series}, 214(2), 25.\\
                 \end{benumerate}
                 

\end{resume}
\end{document}
